
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[letterspace=150]{microtype}
\usepackage{hyperref}

%font
\usepackage[familydefault,light]{Chivo} %% Option 'familydefault' only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\footskip = 5pt

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} #2 & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExperienceSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} #2 & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
%\newcommand{\resumeSubSubItem}[1]{}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeExperienceSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeExperienceSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
\begin{tabular}{c}
  \lsstyle
  {\Huge Team 7}\\ 
  Abdi Vicenciodelmoral $\bullet$ Benjamin Eavenson $\bullet$ Dwayne Butler \\
  Muniker Aragon $\bullet$ Pavel Roslyy $\bullet$ Trever Hibbs \\
\end{tabular}
\end{center}

%--------PROGRAMMING SKILLS------------
\section{\Large{\textbf{Programming Skills}}}

  \resumeSubHeadingListStart
    \item[]{
      \textbf{Languages}{: Python, C, PHP, HTML, CSS}
      \hfill
      \textbf{Technologies}{: Linux, Git, Make, Django, SQL}
    }
    \item[]{
      \textbf{Web-Development}{: React, JavaScript, PHP, Django, HTML, CSS}
    }
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\Large{\textbf{Projects}}}

\resumeSubHeadingListStart

% Example project entry
%===Title Of Project===%
%  \resumeSubheading{Title of Project}{}{technologies used}{short description}
%                   {start and end dates, i.e. August 2019 - August 2020}
%  \resumeItemListStart
%    \resumeSubItem{bold title of bullet1}{bullet 1}
%    \resumeSubItem{bold title of bullet2}{bullet 2}
%    \resumeSubItem{bold title of bullet3}{bullet 3}
%  \resumeItemListEnd
  
  
%===MarketWatch application===%
  \resumeSubheading{MarketWatch}{\href{http://marketwatchfree.com/}{(link)}}{React,Nodejs, AWS}{Ecommerce Management System}{}
    \resumeItemListStart
      \resumeSubItem{}{Develop a full-stack application to automate, monitor, and optimize online shopping.}
      %TODO add technical details to bullet
      \resumeSubItem{}{Implemented Oauth industry-standard protocol to manage user authorization and resource access.}
      \resumeSubItem{}{Developed scheduling system to update user products in short and effective time lapses.}
      \resumeSubItem{}{Launched application into production using AWS, nginx and DNS registering system.}
    \resumeItemListEnd

%===p_scrape===%
  \resumeSubheading{pscrape}{\href{https://github.com/munikeraragon/p_scrape}{(link)}}{React,Nodejs, AWS}{High level Web Scraping Utility}{}
    \resumeItemListStart
      %TODO add technical details to bullet
      \resumeSubItem{}{Developed a Web-Scraping server to process and manage web scraping requests.}
      \resumeSubItem{}{Implemented proxies and user-agent rotation to improve scraping performance.}
      \resumeSubItem{}{Wrote scripts to automate the maintenance and updates of user-agents and proxies in the database.}
    \resumeItemListEnd
  
%===FTP system===%
  \resumeSubheading{FTP Server Client System}{}{C, Linux}{Server and Client implementation of the FTP protocol}{}
    \resumeItemListStart
      \resumeSubItem{}{Designed FTP system that transfers binary data}
      %TODO add technical details to bullet
      \resumeSubItem{}{Durable design anticipates failure and responds gracefully}
      \resumeSubItem{}{Uses low level C socket functions and linux system calls}
    \resumeItemListEnd

%===Compression system===%
  \resumeSubheading{LZW Encoder And Decoder}{}{C, Linux}{Implementation of LZW compression algorithm}{}
    \resumeItemListStart
      \resumeSubItem{}{Designed a system for the lossless compression of binary data}
      \resumeSubItem{}{Considered efficiency of input and output by minimizing the number of writes required to encode/decode}
      \resumeSubItem{}{Uses Low level C functions and manual memory management}
    \resumeItemListEnd
                                      
%===Resume Web-app===%
  \resumeSubheading{Resume Web-app}{\href{http://www.treverhibbs.com/}{(link)}}{django, bootstrap4, css, html}{My resume displayed as a website}{}
    \resumeItemListStart
      \resumeSubItem{}{Designed a easily maintainable website with the model view controller model}
      \resumeSubItem{}{Created a model system for generation of content through database row iteration}
      \resumeSubItem{}{Utilized bootstrap 4 to create styling compatible with most screen sizes}
    \resumeItemListEnd

%===CI club website===%
  \resumeSubheading{Computer Integration Club Website}{\href{http://www6.encs.vancouver.wsu.edu/}{(link)}}{php, css, html, sql}{Website for a University club}{}
    \resumeItemListStart
      \resumeSubItem{}{Designed a css system that made full use of css grid, css flex box, and utility classes}
      \resumeSubItem{}{Created secure php enabled web form}
      \resumeSubItem{}{Made heavy use of git for team coordination including the maintenance of several git branches and the resolution of merge conflicts}
      \resumeSubItem{}{Designed database schema with mysql}
    \resumeItemListEnd

%===B+ Tree Visualization Tool===%
  \resumeSubheading{B+ Tree Visualization Tool}{\href{https://github.com/TreverHibbs/BPlusTree}{(link)}}{js, css, html}{A web app for the dynamic visualization of the B+ Tree data structure and its algorithms}{}
    \resumeItemListStart
      \resumeSubItem{}{Designed the architecture of a view component of a model, view, controller web app}
      \resumeSubItem{}{Created a view module that renders a B+ Tree data structure algorithm}
      \resumeSubItem{}{Made heavy use of JavaScript's functional programming paradigm}
      \resumeSubItem{}{Tested JavaScript functions with mocha and chai frameworks}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{\Large{\textbf{Relevant Experience}}}

  \resumeSubHeadingListStart
    \resumeExperienceSubheading
    {Computer Integration Club}{\href{http://www6.encs.vancouver.wsu.edu/}{(link)}}{Washington State University}
    {Vice President}{August 2019 - Present}
      \resumeItemListStart
		    \resumeItem{Full Stack Web Development}{Designed and implemented all front-end and back-end systems for club website.}
        \resumeItem{Website Hosting With Apache}{Setup Apache, Git, SQL, and created classes for communication between PHP, the database, and  front end template engine.}
        \resumeItem{Secure Login and Database}{Utilized encryption algorithms to generate password hashes and used back-end validation techniques to prevent SQL injection to keep self developed login system secure.}
        \resumeItem{Team Development}{Identified key features of site to create tasks for each member to coordinate development.}
      \resumeItemListEnd
      
    \resumeExperienceSubheading
    {CIMLS} {\href{https://www.cimls.com/}{(link)}}{e1Solutions}
    {Intern}{July 2017 - Present}
      \resumeItemListStart
        \resumeItem{RESTful backend}{Developed class to integrate Census Bureau API for demographics system on site.}
        \resumeItem{Daily Cron Jobs}{Created cron scripts to maintain site and document site statistics.}
        \resumeItem{Google Recaptcha}{Developed class to integrate Google Recaptcha V3 into forms across the site to prevent bot access.}
        \resumeItem{SEO Improvement}{Implemented SEO best practices as outlined by Google, including maintaining canonical urls, using proper breadcrumbs, and modifying content to fit user need.}
        \resumeItem{Development of ccrealtygroup}{Setup git, database, and backend libraries to make code base modular and reusable.}
        \resumeItem{Overhaul JS Minification}{Wrote Makefile to minifiy JavaScript files using Google Closure Compiler with advanced optimizations.}
        \resumeItem{Improve Payment System}{Redesigned the payment system, and switched the payment processor to Stripe.}
        \resumeItem{Database Optimization}{Reduced page loading times by improving SQL queries and table indexes.}
      \resumeItemListEnd
  
    \resumeExperienceSubheading
    {Software Engineer Internship}{}{The Freshwater Trust}
    {Intern}{July 2020  - Present}
       \resumeItemListStart
    		\resumeItem{Mentoring}{Contributed software engineering expertise to an Analytics team.}
    		\resumeItem{Full-stack Web Application}{Assisted in development using Node.js, React.js, and Mapbox to support the decision making of potential investors.}
         \resumeItem{Server and UI Development}{Developed application for data maintenance of a database system.} 
         \resumeItem{Refined Methodologies}{Refinements in System Design, Containerized Applications, and Software Documentation enhanced the readability and maintenance of software.}
       \resumeItemListEnd

    \resumeExperienceSubheading
    {Summer Research Internship}  {}{Washington State University}
    {Intern}{May 2019 - August 2019}
       \resumeItemListStart
         \resumeItem{Deadlocking Research}{Contributed to research aimed at determining whether computer processes can be accurately classified as being "deadlocked".}
         \resumeItem{Data Extraction and Manipulation}{Extracted and manipulated data of computational processes, based on CPU usage. }
         \resumeItem{95\% Accurate Machine Learning Model}{Constructed the model that consumed extracted data to output classification predictions.}
       \resumeItemListEnd

%== ACM-W Club ==%
    \resumeExperienceSubheading
    {ACM-W Club}{}{Washington State University}
    {Vice President}{August 2019 - Present}
      \resumeItemListStart
        \resumeItem{Python Boot-camp}{Contributed slides on mutation to a curriculum covering the basic features of python}
        \resumeItem{Meeting leader}{Gave lectures on security topics and guided club members through practical examples}
        \resumeItem{Vice Presidency}{As long time member elected vice president for 2020 school year}  
    \resumeItemListEnd

  \resumeSubHeadingListEnd
 



%-------------------------------------------
\end{document}



%-------------------------------------------
\end{document}

